Single Site, Single Disturbance, MultiPool

### 2020-11-17 SingleSite_SingleDisturb_MultiPool.Rmd
Added multi.ens.adj function to update disturbance class assigments and state variables

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(BayesianTools)
set.seed(42)
```

@@

```{r}
tobit <- function(x){
  x[x < 0] <- 0
  x
}

@@

  ## draw new IC     *** REPLACE WITH ENSEMBLE ADJUSTMENT ***
  sel.ic <- sample.int(nrow(dat), ne, replace=TRUE)
  Na <- dat[sel.ic,nsel]

  ## EnKF Analysis
  I = H <- diag(rep(1,3))
  K <- PfK %*% t(H) %*% solve(H%*%PfK%*%t(H) + R)
  muaK <- mufK + K%*%(No[t,] - mufK) 
  PaK <- (I-K %*% H)%*%PfK    
  paK = solve(PaK)
  NaK <- PEcAn.assim.sequential::adj.ens(Pf = PfK,X = NfK,mu.f = mufK,mu.a = muaK,Pa = PaK)
  Analysis.KD[[t]] <- list(mua=muaK,pa=paK,Pa=PaK,Na=NaK)

@@

  ## draw new IC     *** REPLACED WITH ENSEMBLE ADJUSTMENT ***
#  Na <- mvtnorm::rmvnorm(ne,mua,Pa)
  Na <- PEcAn.assim.sequential::adj.ens(Pf = Pf,X = Nf,mu.f = muf,mu.a = mua,Pa = Pa)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(BayesianTools)
library(magrittr)
set.seed(42)
```

@@

```{r}
source("multi.ens.adj.R")

tobit <- function(x){
  x[x < 0] <- 0
  x
}

@@

  ## draw new IC
  Na <- multi.ens.adj(
          Xf   = Nf,
          cf   = d.prior,
          mu.f = rbind(priors$mufN,priors$mufD),
          Pf   = abind::abind(solve(priors$pfN),
                 solve(priors$pfD),
                 along=3),
          Xa = dat[,nsel],
          ca = dat[,"D"])
  Ca <- Na[,1] ## updated class assignments
  Na <- tobit(Na[,-1])
#  sel.ic <- sample.int(nrow(dat), ne, replace=TRUE)
#  Na <- dat[sel.ic,nsel]

  ## EnKF Analysis
  I = H <- diag(rep(1,3))
  K <- PfK %*% t(H) %*% solve(H%*%PfK%*%t(H) + R)
  muaK <- mufK + K%*%(No[t,] - mufK) 
  PaK <- (I-K %*% H)%*%PfK    
  paK = solve(PaK)
  NaK <- PEcAn.assim.sequential::adj.ens(Pf = PfK,X = NfK,mu.f = mufK,mu.a = muaK,Pa = PaK) %>% as.matrix()
  Analysis.KD[[t]] <- list(mua=muaK,pa=paK,Pa=PaK,Na=NaK)

@@

  ## draw new IC
  #  Na <- mvtnorm::rmvnorm(ne,mua,Pa)
  Na <- PEcAn.assim.sequential::adj.ens(
    Pf = Pf,X = Nf,mu.f = muf,mu.a = mua,Pa = Pa)
